Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-10 paper/paper.tex
fixed two small symbol typos

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
All PCR amplifications were performed using Kapa HiFi Hotstart Readymix.
1ng of full-length 10x-barcoded cDNA was used as template in a multiplex PCR reaction using  eight segment-specific 5' primers and a shared, 10x-specific 3' primer.
To reduce strand-exchange and generate more even amplification across segments, this reaction was performed in an emulsion PCR using the Micellula DNA Emulsion Kit from Roboklon, supplementing our PCR reaction with additional BSA to a final concentration of 0.1mg/ml.
For all emulsion PCRs, 30 rounds of PCR was performed in order to saturate emulsion materials---unlike open PCR reactions, the physical occlusion of amplified material reduces artifacts at high cycle numbers.
This amplified material was then subjected to eight, individual, emulsion PCR reactions, each using only a single segment-specific 5' primer as well as the common 10x-specific 3' primer, using 1ng of material in each reaction.
This material was pooled to try and obtain an equimolar ratio of segments and sequenced in one SMRTcell in the PacBio RSII, and one SMRTcell of the PacBio Sequel. 
All remaining SMRT-sequencing described in this section was performed on the PacBio Sequel.
To reduce biases in segment representation, we repooled this material and ran another SMRTcell consisting of only HA, NP, NA, M, and NS  segments, and two SMRTcells consisting of PB2, PB1, and PA segments. 
As our depth on the three longest segments remained low, we further amplified our already-amplified material using a non-emulsion PCR using standard conditions for PB2, PB1, and PA, and subjecting the resulting material to a rigorous SPRI-bead selection using SPRIselect beads at a bead-PCR volume ratio of 0.4. 
All non-emulsion PCRs were recovered at sub $/{\mu}$g yields to prevent the occurrence of artifacts at PCR saturation.
We sequenced this bead-selected and repooled material on an additional SMRTcell.
Finally, to improve recovery of full-length PB1, PB2, and PA due to over-representation of internally deleted sequences deriving from defective viruses, we first used our already-amplified segment-specific material in a low-cycle PCR to append circularization adapters, circularized 10ng of this material using NEBuilder in a 20µl reaction volume using an extended reaction time of 50 minutes, incubated these reactions a further 1 hour at 37$^{\circ}$C with exonuclease V to remove linear concatemers and uncircularized material, and bead-cleaned using SPRIselect beads at a volume ratio of 0.4.
This circularized material was then used in three non-emulsion PCRs specific to PB2, PB1, and PA, using two segment-specific primers that align to the central portion of each gene but in apposition to one-another, and bead-cleaned using 0.4 volumes.
This results in successful amplification only if the central portion of the gene is deleted, and if the cDNA is circularized, while still amplifying across cell-specific barcode regions. 
This material was pooled to produce an equimolar mixture of full-length PB1, PA, and PB2 and sequenced in an additional SMRTcell in the PacBio Sequel.

>>>>

\subsection{Enrichment and preparation of viral cDNA for PacBio sequencing}
All PCR amplifications were performed using Kapa HiFi Hotstart Readymix.
1ng of full-length 10x-barcoded cDNA was used as template in a multiplex PCR reaction using  eight segment-specific 5' primers and a shared, 10x-specific 3' primer.
To reduce strand-exchange and generate more even amplification across segments, this reaction was performed in an emulsion PCR using the Micellula DNA Emulsion Kit from Roboklon, supplementing our PCR reaction with additional BSA to a final concentration of 0.1mg/ml.
For all emulsion PCRs, 30 rounds of PCR was performed in order to saturate emulsion materials---unlike open PCR reactions, the physical occlusion of amplified material reduces artifacts at high cycle numbers.
This amplified material was then subjected to eight, individual, emulsion PCR reactions, each using only a single segment-specific 5' primer as well as the common 10x-specific 3' primer, using 1ng of material in each reaction.
This material was pooled to try and obtain an equimolar ratio of segments and sequenced in one SMRTcell in the PacBio RSII, and one SMRTcell of the PacBio Sequel. 
All remaining SMRT-sequencing described in this section was performed on the PacBio Sequel.
To reduce biases in segment representation, we repooled this material and ran another SMRTcell consisting of only HA, NP, NA, M, and NS  segments, and two SMRTcells consisting of PB2, PB1, and PA segments.

As our depth on the three longest segments remained low, we further amplified our already-amplified material using a non-emulsion PCR using standard conditions for PB2, PB1, and PA, and subjecting the resulting material to a rigorous SPRI-bead selection using SPRIselect beads at a bead-PCR volume ratio of 0.4. 
All non-emulsion PCRs were recovered at sub ${\mu}$g yields to prevent the occurrence of artifacts at PCR saturation.
We sequenced this bead-selected and repooled material on an additional SMRTcell.
Finally, to improve recovery of full-length PB1, PB2, and PA due to over-representation of internally deleted sequences deriving from defective viruses, we first used our already-amplified segment-specific material in a low-cycle PCR to append circularization adapters, circularized 10ng of this material using NEBuilder in a 20${\mu}$l reaction volume using an extended reaction time of 50 minutes, incubated these reactions a further 1 hour at 37$^{\circ}$C with exonuclease V to remove linear concatemers and uncircularized material, and bead-cleaned using SPRIselect beads at a volume ratio of 0.4.
This circularized material was then used in three non-emulsion PCRs specific to PB2, PB1, and PA, using two segment-specific primers that align to the central portion of each gene but in apposition to one-another, and bead-cleaned using 0.4 volumes.
This results in successful amplification only if the central portion of the gene is deleted, and if the cDNA is circularized, while still amplifying across cell-specific barcode regions. 
This material was pooled to produce an equimolar mixture of full-length PB1, PA, and PB2 and sequenced in an additional SMRTcell in the PacBio Sequel.
